PM Mungbean meta-analysis

### 2021-02-04 02_Preliminary_analysis.Rmd
small corrections to rain inspection

```{r mid_rain}
PM_MB_dat$mid_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = ymd(x["first_sign_disease"]) + days(30),
         end = ymd(x["first_sign_disease"]) + days(70)
      )
   })

@@

>>>>

```{r mid_rain}
PM_MB_dat$mid_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = ymd(x["planting_date"]) + days(0),
         end = ymd(x["planting_date"]) + days(63)
      )
   })

@@

```{r lm_mid_rain}
summary(lm(grain_yield.t.ha. ~ mid_rain, data = PM_MB_dat))
```
